\cvsection{Experience}

\begin{cventries}
  \cventry
    {Working Student - Research Staff} % Job title
    {TUM - EDA Department} % Organization
    {Munich, Germany} % Location
    {Jul 2022 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          Aiding current research at the department. Work consists of development of projects currently being
          pursued by the deparment. Differs on a project to project basis, but currently has mostly been
          writing python code to automate and build a design space exploration framework that obtains
          benchmarking and other metrics of machine learning models being deployed onto various embedded devices.
      \end{cvitems}
    }
  \cventry
    {Working Student - Embedded Software Engineer} % Job title
    {Molabo Gmbh} % Organization
    {Munich, Germany} % Location
    {Aug 2021 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of}
            \begin{itemize}
                \item {containerized unit tests in C++ through gTest/GoogleTest}
                \item {embedded C code for microcontrollers}
                \item {VHDL Modules for FPGAs}
                \item {build Systems and toolchains written in CMake and Make using Dockers}
                \item {CI pipelines through Jenkinsfiles and groovy scripts}
                \item {Python and Bash scripts to automate development.}
            \end{itemize}
        \item {Supervision of:}
          \begin{itemize}
            \item {the team's CI Pipeline using Jenkins.}
          \end{itemize}
      \end{cvitems}
    }

  % \cventry
  %   {Embedded Software Engineer} % Job title
  %   {Molabo Gmbh} % Organization
  %   {Munich, Germany} % Location
  %   {Aug 2021 - Sept 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Summer Internship at Molabo GMBH.}
  %       \item {I was responsible for unit-tests with Google Test, generating
  %             code coverage, and toolchain development with CMake of their Embedded Software.}
  %     \end{cvitems}
  %   }

  \cventry
    {Tutor - Embedded Systems Programming Lab} % Job title
    {TU München} % Organization
    {Munich, Germany} % Location
    {April 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted students during their course work and their final project, which consisted of writing FreeRTOS applications in C.}
      \end{cvitems}
    }

  \cventry
    {Research Internship} % Job title
    {TU München, RCS Department} % Organization
    {Munich, Germany} % Location
    {Oct. 2020 - Feb 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted a doctorate candidate on his work with tinyML research.}
        \item {Worked with Google’s Edge Coral TPU, where I benchmarked it's
               performance on the inference of several Machine Learning Models.}
        \item {Automated the training, freezing, inference and Hardware deployment of several ML Models.}
      \end{cvitems}
    }

  % \cventry
  %   {Internship} % Job title
  %   {TU München} % Organization
  %   {Munich, Germany} % Location
  %   {Aug. 2019 - Dec. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Research Intern at the Communication Networks Department at TUM. }
  %       \item {I was responsible for testing, debugging and analyzing the behavior
  %              of a software switch within a Software-Defined Network environment.}
  %     \end{cvitems}
  %   }

  % \cventry
  %   {} % Job title
  %   {} % Organization
  %   {} % Location
  %   {} % Date(s)
  %   { }
\end{cventries}
